---
title: "Getting Started with binomial"
author: "Arash Nassirinia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, message = F}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
library(ggplot2)
```

##Binomial

The R package binomial has functions that calculate probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

##Private Functions
There are three functions used that return true or return an error:
check_trials, check_prob, and check_successes

these are used in the main functions. 

##Main Functions 
For example, the function bin_distribution gives us the probability distribution of success. For example, we can do:
```{r}
d<-bin_distribution(trials = 5, prob = 0.5)
d
```
We can then plot it using the plot method:
```{r}
plot(d)
```
the function bin_cumulative does the same thing but also includes the cumulative probability (adding to one in the last row). For example:
```{r}
c<-bin_cumulative(trials = 5, prob = 0.5)
plot(c)
```

We also make the function bin_variable that returns a "binvar" or binomial random variable object that is a list of the trials and probability. Calling the summary method, we are able to see even more information:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

Lastly, we have the main functions for each of the summary measures like bin_mean and bin_variance:
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
```
